---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
```

```{css}
body {
  background: linear-gradient(135deg, #eef2ff 0%, #fdf2f8 100%);
  background-attachment: fixed; 
  font-family: -apple-system, BlinkMacSystemFont, "Segoe UI", Roboto, Helvetica, Arial, sans-serif;
  color: #1f2937;
  margin: 0;
  padding: 40px 20px;
}

.report-card {
  background: rgba(255, 255, 255, 0.85);
  backdrop-filter: blur(12px); 
  margin: 0 auto;            
  padding: 40px;
  border-radius: 24px;
  box-shadow: 0 10px 40px rgba(0, 0, 0, 0.08); 
  border: 1px solid rgba(255, 255, 255, 0.4);
  transition: transform 0.3s ease;
  max-width: 800px;
}

.report-card:hover {
  transform: translateY(-5px); 
}

h2 {
  font-size: 1.8em;
  font-weight: 700;
  background: linear-gradient(90deg, #6366f1, #f43f5e);
  -webkit-background-clip: text;
  -webkit-text-fill-color: transparent;
  margin-top: 0; 
  border-bottom: 1px solid rgba(0,0,0,0.05);
  padding-bottom: 10px;
}

h3 {
  color: #6366f1;
  font-weight: 600;
  margin-top: 30px;
}

img {
  max-width: 100%;
  height: auto;
  border-radius: 12px;
  margin: 20px 0;
  display: block;
  box-shadow: 0 4px 12px rgba(0,0,0,0.05);
}

.dynamic-text {
  font-weight: 700;
  color: #ec4899;
  background: rgba(236, 72, 153, 0.1);
  padding: 2px 8px;
  border-radius: 6px;
}
```

<div class="report-card">

## Observational Logging of Video Consumption

The data I collected comes from a Google Form tracking my daily video consumption habits. It includes information about the type of videos I watch, the duration, the devices I use, and my subjective rating of the audiovisual quality.

```{r data-import-and-summary}
library(tidyverse)

csv_url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vRbOviXondmj168y3_6LPF_RSh00aQlFdERVjgg3t_4knTCD-vK9eObUbdlnKZZXRrv4Ehc9C5Z5K5k/pub?output=csv"
logged_data <- read_csv(csv_url)
#logged_data <- read_csv("data.csv")

latest_data <- logged_data %>%
  rename(
    timestamp = 1,
    video_type = 2,
    video_title = 3,
    duration_min = 4,
    device = 5,
    focus_level = 6,
    quality_rating = 7
  )

# Extract summary values
total_obs <- nrow(latest_data)
avg_duration <- round(mean(latest_data$duration_min, na.rm = TRUE), 1)
```

### Dynamic Summary

So far, I have logged a total of <span class="dynamic-text">`r total_obs`</span> video viewing sessions.

The average time I spent per video session is roughly <span class="dynamic-text">`r paste(avg_duration)`</span> minutes. This metric helps me understand if I am leaning towards short-form content or long-form media like films.

### Visualizing the Data

```{r plot-1}
latest_data %>%
  ggplot(aes(x = video_type, fill = video_type)) +
  # Increase transparency (alpha) and adjust bar width to improve aesthetics
  geom_bar(show.legend = FALSE, alpha = 0.9, width = 0.65) +
  # Use modern color palette (Tailwind CSS style)
  scale_fill_manual(values = c("#6366f1", "#f43f5e", "#10b981", "#f59e0b", "#8b5cf6", "#3b82f6", "#ec4899", "#94a3b8")) +
  # Automatically wrap long labels across multiple lines to prevent layout disruption
  scale_x_discrete(labels = function(x) stringr::str_wrap(x, width = 12)) +
  labs(
    title = "Observation Count by Video Type", 
    x = "Content Type", 
    y = "Count"
  ) +
  theme_minimal() +
  theme(
    # Rotate labels by 45 degrees, adjust alignment, and change font color
    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 10, color = "#4b5563"),
    axis.text.y = element_text(color = "#4b5563"),
    # Remove vertical grid lines to emphasize the data bars
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank(),
    plot.title = element_text(face = "bold", size = 15, color = "#1f2937", margin = margin(b = 15))
  )
```

This first bar chart illustrates the frequency of different video types I watched.

```{r plot-2}
# Plot 2: Average watch duration by content type (using geom_col and sorting in descending order)
latest_data %>%
  group_by(video_type) %>%
  summarise(avg_dur = mean(duration_min, na.rm = TRUE)) %>%
  ggplot(aes(x = reorder(video_type, -avg_dur), y = avg_dur, fill = video_type)) +
  geom_col(show.legend = FALSE, alpha = 0.85, width = 0.65) +
  scale_fill_manual(values = c("#f43f5e", "#6366f1", "#8b5cf6", "#10b981", "#f59e0b", "#ec4899", "#3b82f6")) +
  scale_x_discrete(labels = function(x) stringr::str_wrap(x, width = 12)) +
  labs(
    title = "Average Watch Duration by Content Type", 
    x = "Content Type", 
    y = "Average Duration (Minutes)"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 10, color = "#4b5563"),
    axis.text.y = element_text(color = "#4b5563"),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank(),
    plot.title = element_text(face = "bold", size = 15, color = "#1f2937", margin = margin(b = 15))
  )
```

By calculating the average duration per content type, this second chart provides deeper insight into time allocation. For instance, it highlights which type of media requires the most sustained attention.

```{r plot-top-5}
# Data preparation: Filter the top 5 longest videos and wrap long titles
top_5_duration <- latest_data %>%
  arrange(desc(duration_min)) %>%
  slice_head(n = 5) %>%
  # Wrap long video titles automatically to prevent layout compression
  mutate(video_title_wrapped = stringr::str_wrap(video_title, width = 25))

# Create a horizontal bar chart with thin bars
ggplot(top_5_duration, aes(x = duration_min, y = reorder(video_title_wrapped, duration_min))) +
  # Set fill color to match Indigo theme, adjust width for thinner bars
  geom_col(fill = "#6366f1", alpha = 0.85, width = 0.5) +
  theme_minimal() +
  labs(
    title = "Top 5 Videos by Duration",
    x = "Watch Duration (Minutes)",
    y = "Video Title"
  ) +
  theme(
    axis.text.x = element_text(color = "#4b5563"),
    # Left-align y-axis text and adjust spacing
    axis.text.y = element_text(color = "#4b5563", hjust = 1, vjust = 0.5, size = 9),
    # Remove vertical grid lines to emphasize horizontal comparison
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    plot.title = element_text(face = "bold", size = 15, color = "#1f2937", margin = margin(b = 15))
  )
```

Analyzing individual sessions allows me to identify the most time-consuming content in my log. This horizontal bar chart highlights the 5 videos with the longest watch duration.

```{r plot-3}
# Plot 3: Distribution of audiovisual quality ratings
latest_data %>%
  ggplot(aes(x = as.factor(quality_rating))) +
  geom_bar(fill = "#6366f1", alpha = 0.85, width = 0.5) +
  labs(
    title = "Distribution of Audiovisual Quality Ratings", 
    x = "Subjective Rating (1 = Terrible, 5 = Great)", 
    y = "Count"
  ) +
  theme_minimal() +
  theme(
    axis.text = element_text(color = "#4b5563"),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank(),
    plot.title = element_text(face = "bold", size = 15, color = "#1f2937", margin = margin(b = 15))
  )
```

Finally, the third chart displays the distribution of my subjective audiovisual quality ratings across all logged sessions.

</div>
